\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-04-01 grassposter/2015_EGU_G7_Python/listings/pygrass_raster_examples.tex
rewrite Highlights, parser box, IPython box, revert temporal box to https://trac.osgeo.org/grass/changeset/64917 and other improvements
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64967 15284696-431f-4ddb-bdfa-cd5b030d7da7

def numpy2raster(array, mtype, name):
    """Save a numpy array to a raster map"""
    reg = Region()
    if (reg.rows, reg.cols) != array.shape:
        msg = "Region and array shape are different: %r != %r"
        raise TypeError(msg % ((reg.rows, reg.cols), array.shape))
    with RasterRow(name, mode='w', mtype=mtype) as new:
        newrow = Buffer((array.shape[1],), mtype=mtype)
        for row in array:
            newrow[:] = row[:]   # cast array to raster type
            new.put_row(newrow)  # write row to raster map
\end{lstlisting}
\end{document}

>>>>

def numpy2raster(array, mtype, name):
    """Save a numpy array to a raster map"""
    reg = Region()
    if (reg.rows, reg.cols) != array.shape:
        msg = "Region and array shape are different: %r != %r"
        raise TypeError(msg % ((reg.rows, reg.cols), array.shape))
    with RasterRow(name, mode='w', mtype=mtype) as new:
        newrow = Buffer((array.shape[1],), mtype=mtype)
        for row in array:
            newrow[:] = row[:]  # cast array to raster type
            new.put_row(newrow)  # write row to raster map
# note that there is a specialized package which implements this functionality
\end{lstlisting}
\end{document}

### 2015-04-01 grassposter/2015_EGU_G7_Python/main.tex
rewrite Highlights, parser box, IPython box, revert temporal box to https://trac.osgeo.org/grass/changeset/64917 and other improvements
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64967 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Highlights}}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS \cite{Neteler2012} is a platform for geospatial computations.
% \item GRASS GIS used directly using Python or GUI or through other software.
\item The functionality is divided into set of modules (individual tools, functions, algorithms or models).
\item Core libraries and algorithms implemented in C for high performance.
\item Python APIs for GRASS GIS are an interface for both the modules and the library.
\item Standardization of inputs and interface serves as a tool for integration a sharing.
\item Other Python tools such as NumPy or IPython can be used together with GRASS GIS.
% \item The system together with the broad community ensures long term preservation of algorithms.
% \item GRASS GIS ecosystem supports code maintenance.
% \end{itemize}
}

@@

The g.parser module provides full parser support for GRASS GIS scripts.
It provides the creation of help page template, and command line option
checking. Each command and scripts which uses the GRASS GIS parser can
publish its parameter and flags description in XML. Through the included
XML parser this description can be turned into a graphical user interface with
standardized styling.

@@

\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_gui}
\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_cli}

@@

\block{\blocktitlewrap{GRASS Scripting library interface to GRASS GIS modules}}{

@@

Documentation of GRASS GIS modules usually use Bash syntax for examples:

@@

These can be easily rewritten to \pkg{grass.script} or \pkg{grass.pygrass} syntax shown above.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Using IPython Notebook}}{

	IPython Notebook is a web-based application that provides a tool to: developing, documenting, and executing code, as well as communicating the results.
	One great tool to process and visualize your data/maps, integrating formulas and explanatory text, interacting with remote server and clusters.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to C libraries}}{
Some API examples to convert a raster map to a NumPy array and then back to a raster.

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_raster_examples}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Testing the code}}{
% To facilitate the development of the module, GRASS GIS provides
% a Python library for testing (Petras and Gebbert, 2014)
% which helps researchers to ensure the robustness of the
% algorithm, correctness of the results in edge cases
% as well as the detection of changes in results due to new
% development.

@@

\includegraphics[width=\linewidth, clip, trim=0 5 0 0]{gunittest}

% Tests can be written to check the numerical results but also general functionality
% such as if different parameters are accepted.
Tests can use standardize datasets or use custom reference data.
Basic tests can also just look at the statistical summary of a result.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
A Python script can by turned into a GRASS GIS modules by adding a definition of the interface.
Also, GRASS GIS modules expect to be executed in GRASS GIS session.
Python scripts which are using GRASS GIS can be written in a way that GRASS GIS session is not required;
the setup of a necessary environment is done in the script itself.
% running code from IDE

The GRASS GIS Addon repository ensures vendor-independent long-term preservation of the code
and ensures an easy distribution of module to individual users.
Well maintained modules in Addons can be moved to GRASS GIS core.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS 7 Temporal Framework}}{
The GRASS GIS Temporal Framework offers the temporal GIS functionality of GRASS GIS 
and provides a Python API to implement spatio-temporal processing modules. 
The framework introduces space-time datasets that represent time series of raster, 
3D raster or vector maps. Some API examples:
\includegraphics[width=1\linewidth, clip, trim=0 0 0 0]{tgrass_examples}
}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{osgeo}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
GRASS GIS is a OSGeo project. OSGeo provides infrastructure for project
Web sites, mailing lists and source code management.
\end{minipage}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{google}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code 2014.
\end{minipage}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Highlights}}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.9ex}}
\item GRASS GIS \cite{Neteler2012} is a platform for geospatial computations.
% \item GRASS GIS used directly using Python or GUI or through other software.
\item The functionality is divided into a set of modules (individual tools, functions, algorithms or models).
\item Core libraries and algorithms implemented in C for high performance.
\item Both the modules and the libraries are accessible through the Python API.
\item Specialized Python APIs support different use cases ranging from high level scripting to fine data editing.
\item It is simple to build graphical user interface.
\item NumPy or IPython can be used together with GRASS GIS Python APIs.
% \item The system together with the broad community ensures long term preservation of algorithms.
% \item GRASS GIS ecosystem supports code maintenance.
% \end{itemize}
}

@@

The \gmodule{g.parser} module provides full interface definition support for Python scripts
including creation of standardized part of a help page and command line checking.
Each script which uses the GRASS GIS parser can
publish definition of its parameters (options and flags) in XML.
The GRASS GIS graphical user interface is able to use the XML
to dynamically generate an interactive graphical dialog with unified styling.

@@

\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_gui}
~
\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_cli}

@@

\block{\blocktitlewrap{GRASS Scripting Library interface to GRASS GIS modules}}{

@@

Documentation of GRASS GIS modules usually use Bash syntax to provide an example of usage, e.g.:

@@

This syntax can be easily rewritten to the \pkg{grass.script} syntax or the \pkg{grass.pygrass} syntax shown above.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{IPython Notebook}}{

IPython Notebook is a web-based tool to develop, document, and execute code, as well as communicate the results.
In combination with GRASS GIS, it is an excellent tool to process and visualize your geospatial data,
integrate formulas, explanatory text and maps, and interact with remote servers and clusters.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to C libraries}}{
Examples of using the API to convert a raster map to a NumPy array and back to raster:

\includegraphics[width=\linewidth, clip, trim=0 8 0 0]{pygrass_raster_examples}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Testing the algorithms}}{
% To facilitate the development of the module, GRASS GIS provides
% a Python library for testing (Petras and Gebbert, 2014)
% which helps researchers to ensure the robustness of the
% algorithm, correctness of the results in edge cases
% as well as the detection of changes in results due to new
% development.

@@

\includegraphics[width=\linewidth, clip, trim=0 8 0 0]{gunittest}

% Tests can be written to check the numerical results but also general functionality
% such as if different parameters are accepted.
Tests can use standardize datasets or use custom reference data.
It is very easy to write a sophisticated test just by checking a statistical summary of computation results.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
A Python script can by turned into a GRASS GIS module by adding a definition of the interface
using GRASS GIS parser mechanism.
Another difference is that GRASS GIS modules expect to be executed in GRASS GIS session.
Python scripts which are using GRASS GIS can be written in a way that GRASS GIS session is not required;
the setup of a necessary environment is done in the script itself in this case.
% running code from IDE

The GRASS GIS Addon repository contains modules from wide range of contributors
and ensures vendor-independent long-term preservation of the code
and ensures an easy distribution of module to individual users.
Well maintained modules in Addons can be moved to GRASS GIS core.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS Temporal Framework}}{
The GRASS GIS Temporal Framework implements the temporal GIS functionality
and provides a Python API to implement spatio-temporal processing modules.
The framework introduces space-time datasets that represent time series of raster,
3D raster or vector maps.
An API example:
\includegraphics[width=1\linewidth, clip, trim=0 0 0 0]{tgrass_examples}
}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{osgeo}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
GRASS GIS is a OSGeo project. OSGeo provides infrastructure for project
websites, mailing lists and source code management.
\end{minipage}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{google}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code 2012 and 2014.
\end{minipage}
